Constrained Optimization-Based Neuro-Adaptive Control (CONAC) for Weight and Convex Input Constraints

### 2025-05-02 manuscript.tex
1. check the words "simulation" 2. paramters were fixed 3. add the comment for servo

% ------------------------------------
% Controller Parameters
% ------------------------------------
For all controllers ((C$_1$), (C$_2$), and (C$_3$)), the NN input vector ${\q}_n$ was set as ${\q}_n=\left(\q^\top,\dq^\top,\fe^\top,1\right)^\top\in\R^{3n+1}$ with the augmented scalar $1$ included to account for the bias term in the weight matrix. 
The NNs' weights were initialized randomly with uniform distribution in the range of $[-0.5,0.5]$, and the same random seed.
Each NN architecture had two hidden layers with four nodes \DHHO{k=2? (\ie $k=2, l_0=6, l_1=4, l_2=4, l_3=2$)}, and the adaptation gain was set to $\alpha=0.2$.
The filtering matrix $\mm{\Lambda}$ was set to $\mm{\Lambda}=\mydiag([5,15])$.
\DHHO{ simulation?
    The sampling rate of the controller was $250$ Hz considering the real-time implementation, and $1000$ Hz for the simulation.}
\MSRY{CAN Hz?}
To emphasize the control input constraint handling capability, the weight constraint parameters were selected sufficiently large (\ie $\overline\wth_0=11, \overline\wth_1=12$, and $\overline\wth_2=13$), avoiding the violation of the weight constraints.

@@

% ------------------------------------
% Controller Table
% ------------------------------------
\begin{table}[t]
    \renewcommand{\arraystretch}{1.3}
    \caption{Properties of the controllers used in simulation}
    \label{table:controller}
    \centering
    \begin{tabular}{c l l}
    \hline
        \!&\!\bf{Description}\!&\!\bf{Input Constraint}\!\\
    \hline
    \hline
        (C$_1$)\!&\!large $\beta_j$\!&\!$\overline{\tau}=11,\overline{\tau}_2=-\underline{\tau}_2=3.5$ \\
    \hline
        (C$_2$)\!&\!aux. sys.\!&\!$\overline{\tau}_1\!=\!-\underline{\tau}_1\!=\!10.428,\overline{\tau_2}\!=\!-\underline{\tau_2}\!=\!3.5$\!\\
    \hline
        (C$_3$)\!&\!small $\beta_j$\!&\!$\overline{\tau}=11,\overline{\tau}_2=-\underline{\tau_2}=3.5$ \\
    \hline
        (C$_4$)\!&\!no $\rbu$ constraints\!&\!$[\beta_j]_{j\in\{\rbu,\overline{\tau}_2,\underline{\tau}_2\}}=\mv{0}$ \\
    \hline
    \end{tabular}
    \label{table:controllers}
\end{table}

@@

\begin{figure*}[t]
  \centering
    \subfloat[Tracking result of $q_1$.]{
    %   \includegraphics
      \includegraphics[width=\figSizeTwoCol\linewidth]
      {
        % fig/Fig1.pdf
        src/measurement/figures/compare/Fig1.eps
      }%
      \label{fig:ctrl:result:q1}}
    \hfill
    \subfloat[Tracking result of $q_2$.]{
      \includegraphics[width=\figSizeTwoCol\linewidth]
      {
        % src/measurement/figures/compare/Fig11.eps
        src/measurement/figures/compare/Fig2.eps
      }%
      \label{fig:ctrl:result:q2}}
    \vfill
      \subfloat[Control input $\tau_1$.]{
        \includegraphics[width=\figSizeTwoCol\linewidth]
        {
            src/measurement/figures/compare/Fig3.eps
        }%
        \label{fig:ctrl:result:tau:1}}
    \hfill
      \subfloat[Control input $\tau_2$.]{
        \includegraphics[width=\figSizeTwoCol\linewidth]
        {
            src/measurement/figures/compare/Fig4.eps
        }%
        \label{fig:ctrl:result:tau:2}}
        \vfill
    \subfloat[Norm of control input $\rbu$.]{
        \includegraphics[width=\figSizeTwoCol\linewidth]
        {
            src/measurement/figures/compare/Fig5.eps
        }%
        \label{fig:ctrl:result:tau:norm}}
    \hfill
    \subfloat[Norm of weights ${\estwth}_i$.]{
        % \includegraphics
        \includegraphics[width=\figSizeTwoCol\linewidth]
        {
            % fig/Fig7.pdf
            src/measurement/figures/compare/Fig7.eps
        }%
        \label{fig:ctrl:result:weight}}        
    \caption{
  Simulation results of (C$_1$) (blue), (C$_2$) (cyan), (C$_3$) (gray), and reference signal of $\qd$ (red dashed line).
  }
\label{fig:ctrl:result}
\end{figure*}

@@

The simulation results are shown in Fig.~\ref{fig:ctrl:result} and the quantitative comparison of the tracking performance is given in Table~\ref{tab:sim:L2}.
Across the two episodes, all controllers enhanced their tracking performances about 
$60.2 \%$ for (C$_1$), $52.7 \%$ for (C$_2$), and $61.9 \%$ for (C$_3$) in $L_2$ norm of $r_1$, and $84.5 \%$ for (C$_1$), $79.3 \%$ for (C$_2$), and $80.5 \%$ for (C$_3$) in $L_2$ norm of $r_2$, respectively, as shown in Table~\ref{tab:sim:L2}.
Qualitatively, as described in Fig.~\ref{fig:ctrl:result:q1} and Fig.~\ref{fig:ctrl:result:q2}, the oscillations were suppressed in the second episode, as well.
This results lead to the conclusion that the NNs in all controllers were able to learn the ideal control input $\rbu^*$ properly, by the filtered error $\fe$, despite the fact that $\rbu^*$ was not known in advance.
Moreover, since the learning began from the random initialization of the weights and no prior knowledge of the system, the online learning capability of the proposed CONAC was demonstrated.

@@

\color{red}
The KKT conditions defined in \cite[Def. @@]{Nocedal:2006aa} were satisfied in the simulation, as shown in Fig.~\ref{fig:ctrl:result:scope:beta}, where the Lagrange multipliers $\lambda_j,\ \forall j\in\mathcal I$ were positive and the constraint violations $c_j,\ \forall j\in\mathcal I$ were negative.
\color{black}

\subsubsection{Computational Time}
is shown in Fig.~\ref{fig:ctrl:real:result:cmp:time}. The computational time of CONAC was 0.5 ms, which is less than the sampling time of 4 ms. 
This indicates that the proposed CONAC can be implemented in real-time applications.

@@

Simulation results validated the superior performance of CONAC compared to conventional methods, such as DNN-BSC and DNN-BSC-A. CONAC not only handled complex input constraints but also managed the weight norm constraints rigorously, leading to improved tracking accuracy and stability without notable oscillations.

>>>>

% ------------------------------------
% Controller Parameters
% ------------------------------------
For all controllers ((C$_1$), (C$_2$), and (C$_3$)), the NN input vector ${\q}_n$ was set as ${\q}_n=\left(\q^\top,\dq^\top,\fe^\top,1\right)^\top\in\R^{3n+1}$ with the augmented scalar $1$ included to account for the bias term in the weight matrix. 
The NNs' weights were initialized randomly with uniform distribution in the range of $[-0.5,0.5]$, and the same random seed.
Each NN architecture had two hidden layers with four nodes \DHHO{k=2? (\ie $k=2, l_0=6, l_1=4, l_2=4, l_3=2$)}, and the adaptation gain was set to $\alpha=0.2$.
The filtering matrix $\mm{\Lambda}$ was set to $\mm{\Lambda}=\mydiag([5,15])$.
\DHHO{ simulation?
    The sampling rate of the controller was $250$ Hz considering the real-time implementation, and $1000$ Hz for the simulation.}
\MSRY{CAN Hz?}
To emphasize the control input constraint handling capability, the weight constraint parameters were selected sufficiently large (\ie $\overline\wth_0=5.0, \overline\wth_1=5.5$, and $\overline\wth_2=6.0$), avoiding the violation of the weight constraints.

@@

% ------------------------------------
% Controller Table
% ------------------------------------
\begin{table}[t]
    \renewcommand{\arraystretch}{1.3}
    \caption{Properties of the controllers used in \DHHO{sim? simulation}}
    \label{table:controller}
    \centering
    \begin{tabular}{c l l}
    \hline
        \!&\!\bf{Description}\!&\!\bf{Input Constraint}\!\\
    \hline
    \hline
        (C$_1$)\!&\!large $\beta_j$\!&\!$\overline{\tau}=11,\overline{\tau}_2=-\underline{\tau}_2=3.5$ \\
    \hline
        (C$_2$)\!&\!aux. sys.\!&\!$\overline{\tau}_1\!=\!-\underline{\tau}_1\!=\!10.428,\overline{\tau_2}\!=\!-\underline{\tau_2}\!=\!3.5$\!\\
    \hline
        (C$_3$)\!&\!small $\beta_j$\!&\!$\overline{\tau}=11,\overline{\tau}_2=-\underline{\tau_2}=3.5$ \\
    \hline
        (C$_4$)\!&\!no $\rbu$ constraints\!&\!$[\beta_j]_{j\in\{\rbu,\overline{\tau}_2,\underline{\tau}_2\}}=\mv{0}$ \\
    \hline
    \end{tabular}
    \label{table:controllers}
\end{table}

@@

\begin{figure*}[t]
  \centering
    \subfloat[Tracking result of $q_1$.]{
    %   \includegraphics
      \includegraphics[width=\figSizeTwoCol\linewidth]
      {
        % fig/Fig1.pdf
        src/measurement/figures/compare/Fig1.eps
      }%
      \label{fig:ctrl:result:q1}}
    \hfill
    \subfloat[Tracking result of $q_2$.]{
      \includegraphics[width=\figSizeTwoCol\linewidth]
      {
        % src/measurement/figures/compare/Fig11.eps
        src/measurement/figures/compare/Fig2.eps
      }%
      \label{fig:ctrl:result:q2}}
    \vfill
      \subfloat[Control input $\tau_1$.]{
        \includegraphics[width=\figSizeTwoCol\linewidth]
        {
            src/measurement/figures/compare/Fig3.eps
        }%
        \label{fig:ctrl:result:tau:1}}
    \hfill
      \subfloat[Control input $\tau_2$.]{
        \includegraphics[width=\figSizeTwoCol\linewidth]
        {
            src/measurement/figures/compare/Fig4.eps
        }%
        \label{fig:ctrl:result:tau:2}}
        \vfill
    \subfloat[Norm of control input $\rbu$.]{
        \includegraphics[width=\figSizeTwoCol\linewidth]
        {
            src/measurement/figures/compare/Fig5.eps
        }%
        \label{fig:ctrl:result:tau:norm}}
    \hfill
    \subfloat[Norm of weights ${\estwth}_i$.]{
        % \includegraphics
        \includegraphics[width=\figSizeTwoCol\linewidth]
        {
            % fig/Fig7.pdf
            src/measurement/figures/compare/Fig7.eps
        }%
        \label{fig:ctrl:result:weight}}        
    \caption{
  \DHHO{sim?: Simulation} results of (C$_1$) (blue), (C$_2$) (cyan), (C$_3$) (gray), and reference signal of $\qd$ (red dashed line).
  }
\label{fig:ctrl:result}
\end{figure*}

@@

\DHHO{sim? The simulation} results are shown in Fig.~\ref{fig:ctrl:result} and the quantitative comparison of the tracking performance is given in Table~\ref{tab:sim:L2}.
Across the two episodes, all controllers enhanced their tracking performances about 
$60.2 \%$ for (C$_1$), $52.7 \%$ for (C$_2$), and $61.9 \%$ for (C$_3$) in $L_2$ norm of $r_1$, and $84.5 \%$ for (C$_1$), $79.3 \%$ for (C$_2$), and $80.5 \%$ for (C$_3$) in $L_2$ norm of $r_2$, respectively, as shown in Table~\ref{tab:sim:L2}.
Qualitatively, as described in Fig.~\ref{fig:ctrl:result:q1} and Fig.~\ref{fig:ctrl:result:q2}, the oscillations were suppressed in the second episode, as well.
This results lead to the conclusion that the NNs in all controllers were able to learn the ideal control input $\rbu^*$ properly, by the filtered error $\fe$, despite the fact that $\rbu^*$ was not known in advance.
Moreover, since the learning began from the random initialization of the weights and no prior knowledge of the system, the online learning capability of the proposed CONAC was demonstrated.

@@

\color{red}
\DHHO{sim?: The KKT conditions defined in \cite[Def. @@]{Nocedal:2006aa} were satisfied in the simulation}, as shown in Fig.~\ref{fig:ctrl:result:scope:beta}, where the Lagrange multipliers $\lambda_j,\ \forall j\in\mathcal I$ were positive and the constraint violations $c_j,\ \forall j\in\mathcal I$ were negative.
\color{black}

\subsubsection{Computational Time}
is shown in Fig.~\ref{fig:ctrl:real:result:cmp:time}. The computational time of CONAC was 
\DHHO{
    3.4 ms?,} which is less than the sampling time of 4 ms. 
This indicates that the proposed CONAC can be implemented in real-time applications.

@@

\DHHO{sim? : Simulation results} validated the superior performance of CONAC compared to conventional methods, such as DNN-BSC and DNN-BSC-A. CONAC not only handled complex input constraints but also managed the weight norm constraints rigorously, leading to improved tracking accuracy and stability without notable oscillations.
